Staged Abstract Interpreters

### 2019-03-27 paper/10_intro.tex
few typos
misc and reorganize

\vspace{-1em}
\begin{figure}[h]
  \begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em]
  {
    \begin{smallmatrix} \text{unstaged} \\ \text{abstract} \\ \text{interpreters} \\ (\text{Sec.}~\ref{unstaged_abs}) \end{smallmatrix} &
    \begin{smallmatrix} \text{staged} \\ \text{abstract} \\ \text{interpreters} \\ (\text{Sec.}~\ref{sai}) \end{smallmatrix} \\
    \begin{smallmatrix} \text{unstaged} \\ \text{concrete} \\ \text{interpreters} \\ (\text{Sec.}~\ref{prelim}) \end{smallmatrix} &
    \begin{smallmatrix} \text{staged} \\ \text{concrete} \\ \text{interpreters} \\ (\text{Sec.}~\ref{stagedinterp}) \end{smallmatrix} \\ };
  \path[-stealth]
    (m-1-1) edge node [above, font=\scriptsize] {$\updownarrows$} (m-1-2)
    (m-2-1) edge node [left, font=\scriptsize] {$\alpha$} (m-1-1)
    (m-2-1) edge node [below, font=\scriptsize] {$\updownarrows$} (m-2-2)
    (m-2-2) edge node [right, font=\scriptsize] {$\alpha$} (m-1-2);
  \end{tikzpicture}
  \caption{The confluence of specialization and approximation.}
  \label{confluence}
\end{figure}
\vspace{-1em}

@@

The paper is organized as follows:

>>>>

\vspace{-1em}
\begin{figure}[h]
  \begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em]
  {
    \begin{smallmatrix} \text{unstaged} \\ \text{abstract} \\ \text{interpreters} \\ (\text{Sec.}~\ref{unstaged_abs}) \end{smallmatrix} &
    \begin{smallmatrix} \text{staged} \\ \text{abstract} \\ \text{interpreters} \\ (\text{Sec.}~\ref{sai}) \end{smallmatrix} \\
    \begin{smallmatrix} \text{unstaged} \\ \text{concrete} \\ \text{interpreters} \\ (\text{Sec.}~\ref{unstaged_conc}) \end{smallmatrix} &
    \begin{smallmatrix} \text{staged} \\ \text{concrete} \\ \text{interpreters} \\ (\text{Sec.}~\ref{stagedinterp}) \end{smallmatrix} \\ };
  \path[-stealth]
    (m-1-1) edge node [above, font=\scriptsize] {$\updownarrows$} (m-1-2)
    (m-2-1) edge node [left, font=\scriptsize] {$\alpha$} (m-1-1)
    (m-2-1) edge node [below, font=\scriptsize] {$\updownarrows$} (m-2-2)
    (m-2-2) edge node [right, font=\scriptsize] {$\alpha$} (m-1-2);
  \end{tikzpicture}
  \caption{The confluence of specialization and approximation.}
  \label{confluence}
\end{figure}
\vspace{-1em}

@@

The paper is organized as follows: \todo{restate this part}

### 2019-03-27 paper/40_absinterp.tex
misc and reorganize

\begin{lstlisting}
  def lift_nd[T](vs: List[T]): AnsM[T]
  def ap_clo(ev: Expr => Ans)(rator: Value, rand: Value): Ans = for {
    CloV(Lam(x, e), ρ: Env) <- lift_nd[AbsValue](rator.toList)
    α <- alloc(x)
    _ <- set_store(α → rator)
    rt <- ext_env(ev(e))(x → α)
  } yield rt
\end{lstlisting}

>>>>

\begin{lstlisting}
  def lift_nd[T](vs: List[T]): AnsM[T]
  def ap_clo(ev: Expr => Ans)(rator: Value, rand: Value): Ans = for {
    α <- alloc(x)
    CloV(Lam(x, e), ρ: Env) <- lift_nd[AbsValue](rator.toList)
    _ <- set_store(α → rator)
    rt <- ext_env(ev(e))(x → α)
  } yield rt
\end{lstlisting}

### 2019-03-27 paper/50_stageabs.tex
misc and reorganize

\begin{lstlisting}
  def lift_nd[T](vs: Rep[List[T]]): AnsM[T]
  def emit_ap_clo(rator: Rep[AbsValue], rand: Rep[Value], σ: Rep[Store],
                  in: Rep[Cache], out: Rep[Cache]): Rep[(List[(Value, Store)], Cache)]
  def ap_clo(ev: Expr => Ans)(rator: Rep[Value], rand: Rep[Value]): Ans = for {
    clo <- lift_nd[AbsValue](rator.toList)
    σ <- get_store; in <- ask_in_cache; out <- get_out_cache
    val res: Rep[(List[(Value, Store)], Cache)] = emit_ap_clo(clo, rand, σ, in, out)
    _ <- put_out_cache(res._2)
    vs <- lift_nd[(Value, Store)](res._1)
    _ <- put_store(vs._2)
  } yield vs._1
\end{lstlisting}

@@

Our fixed-point iteration again relies on two caches @in@ and @out@, which are
both staged values now. Therefore, the query of whether the @out@ cache contains
the current configuration produces a next-stage Boolean value, i.e.,
@Rep[Boolean]@. Consequently, the branching can not be determined statically --
we need to generate code for @if@. Figure \ref{fig:staged_coind_cache} shows the
staged version of @fix@.

>>>>

\begin{lstlisting}
  def lift_nd[T](vs: Rep[List[T]]): AnsM[T]
  def emit_ap_clo(rator: Rep[AbsValue], rand: Rep[Value], σ: Rep[Store],
                  in: Rep[Cache], out: Rep[Cache]): Rep[(List[(Value, Store)], Cache)]
  def ap_clo(ev: Expr => Ans)(rator: Rep[Value], rand: Rep[Value]): Ans = for {
    σ <- get_store;     clo <- lift_nd[AbsValue](rator.toList)
    in <- ask_in_cache; out <- get_out_cache
    val res: Rep[(List[(Value, Store)], Cache)] = emit_ap_clo(clo, rand, σ, in, out)
    _ <- put_out_cache(res._2)
    vs <- lift_nd[(Value, Store)](res._1)
    _ <- put_store(vs._2)
  } yield vs._1
\end{lstlisting}

@@

Our fixed-point iteration again relies on the two caches @in@ and @out@, which are
both staged values now. Therefore, the query of whether the @out@ cache contains
the current configuration produces a next-stage Boolean value, i.e.,
@Rep[Boolean]@. Consequently, the branching can not be determined statically --
we need to generate code for @if@. Figure \ref{fig:staged_coind_cache} shows the
staged version of @fix@.
